---
title: "BUAN 6356 - Homework 2 - Abhishek"
author: "Abhishek Pandey"
date: "November 2, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Using ggplot2 package to create a scatter plot.

```{r GGplot, echo=FALSE}

library(tidyverse)
library(leaps)
library(caret)
library(gplots)
library(plyr)

SysAdmin.df <- read.csv("SystemAdministrators.csv")

SysAdmin.df$Completed.task <- as.factor(SysAdmin.df$Completed.task)
Completed <- SysAdmin.df$Completed.task

ggplot(SysAdmin.df) + 
  geom_point(aes(x = Experience, y = Training, color = Completed), size = 2) +
  theme_classic()+
  xlab('Experience (Months)') +
  ylab('Training Credits') +
  ggtitle('Experience vs Training') +
  theme(plot.title = element_text(hjust = 0.8)) +
  scale_x_continuous(breaks = pretty(SysAdmin.df$Experience, n = 14))

```

Experience predictor appears potentially useful for classifying task completion as most employees with exp. greater than 8 have completed task. 

# Logistic Regression

```{r Logistic Regression, echo=TRUE}

options(scipen = 1429)

logit.reg <- glm(Completed.task ~ Experience + Training, 
                 data = SysAdmin.df, family = "binomial")

summary(logit.reg)

```

# Confusion Matrix

```{r Confusion Matrix, echo=TRUE}

training.df <- SysAdmin.df
logit.reg.point.pred.training <- predict(logit.reg, data = training.df, type = "response")

training.df$Completed.task <- revalue(training.df$Completed.task, c("Yes"=1))
training.df$Completed.task <- revalue(training.df$Completed.task, c("No"=0))
confusionMatrix(as.factor(as.numeric(logit.reg.point.pred.training>0.5)), training.df$Completed.task)

```

Percentage of programmers incorrectly classified as failing to complete the task > 5*100/15 = 33.33

An experience of 9.14 months must be accumulated by a programmer with 6 years of training before his or her estimated probability of completing the task exceeds 0.6

Calculation:
log(0.6/(1-0.6)) = -10.9813 + 1.1269 x (Experience) + 0.1805 x 6
= 9.14 months